Supplemental Materials

### 2024-06-27 products/manuscript/supplement/Supplemental_Materials.qmd
Update to manuscript
Changed repository name

---
title: "Supplemental Materials"
author: Cassia Roth
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
    bibliography: ../../../assets/Mada_Bib.bib
    csl: ../../../assets/vancouver.csl
---
# Supplemental Materials

@@

In the initial months of publication, the reports included more complete information, including labor time or detailed descriptions of surgical procedures. Over time, clinical notes became streamlined. When physicians intervened in birth, the notes included the type of intervention, the indication, and the obstetrician. For more information on this as a source, see my other publications [@roth2020, @roth2020a].

@@

@@

Test/train (75-25 split) and cross-validation were performed on all models. Model prediction performance did not improve greatly using these tests. Model performance resulted in insignificant results when run on the testing data given the smaller sample size. All code for the train/test analysis and cross-validation analysis can be found in `fullanalysis-v1.qmd`.

>>>>

---
title: "Supplemental Materials"
author: Cassia Roth
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
    bibliography: ../../../assets/Mada_Bib.bib
    csl: ../../../assets/chicago-fullnote-bibliography.csl
---
# Supplemental Materials

## Schematic of workflow

If reproducing this analysis, please run code in the following order: 1) `processingfile-v1.qmd` or `processingcode.R` in the `processing-code` folder; 2) `eda-v1.qmd` or `edacode.R` in the `eda-code` folder; 3) `introanalyis-v1.qmd` or `introanalysis.R` in the `analysis-code` folder; 4) `fullanalysis-v1.qmd` or `fullanalysiscode.R` in the `analysis-code` folder. Please defer to all `.qmd` files as the master over any `.R` files.

## Data import and cleaning

The GitHub repository for this project includes all relevant materials. All discussions of data import are detailed in the files `processingfile-v1.qmd` or `processingcode.R` in the `processing-code` folder. The original raw data, the codebook, and the processed data are available in the `data` folder.

@@

In the initial months of publication, the reports included more complete information, including labor time or detailed descriptions of surgical procedures. Over time, clinical notes became streamlined. When physicians intervened in birth, the notes included the type of intervention, the indication, and the obstetrician. For more information on this as a source, see my other publications [@roth2020; @roth2020a].

@@

To better understand our outcome of interest, birth weight, the exploratory analysis includes the distribution of the data. Figure 1 is a histogram of the birth weight data, with the two dotted red lines marking the upper and lower limits of what the WHO now defines as normal birth weight [@worldhealthorganization2022].

```{r}
#| label: fig-schematic-1
#| fig-cap: Histogram of birth weight
#| echo: FALSE
knitr::include_graphics(here("results","figures","weight_distribution.png"))
```

Because the data are missing gestational age, birth length is less important for our analysis. Nonetheless, Figure 2 shows a histogram of the distribution of birth lengths in the sample. The red line marks the average birth length for both male and female infants (49 centimeters), which is in line with current estimates on birth length globally [@jamshed2020].

```{r}
#| label: fig-schematic-2
#| fig-cap: Histogram of birth length
#| echo: FALSE
knitr::include_graphics(here("results","figures","length_distribution.png"))
```

Figure 3 visualizes the relationship between infant weight and length. Unsurprisingly, birth weight and length are positively correlated.

```{r}
#| label: fig-schematic-3
#| fig-cap: Scatterplot of birth weight by length
#| echo: FALSE
knitr::include_graphics(here("results","figures","length_weight.png"))
```

Finally, Figure 4 visualizes the relationship of birth weight and length, stratified by sex since male infants are usually slightly heavier and longer than females [@crawford1987, @marsal1996].

```{r}
#| label: fig-schematic-4
#| fig-cap: Scatterplot of birth weight by length stratified by sex
#| echo: FALSE
knitr::include_graphics(here("results","figures","length_weight_sex.png"))
```

@@

Given that this study is an inferential, hypothesis-supporting approach that is exploring how specific maternal predictors affect the outcome of interest, birth weight, please see the `fullanalysis-v1.qmd` for all predictive metrics, where test/train and cross-validation were applied to test performance. Model performance did not significantly improve with these additional tests. When run on testing data, most results were insignificant.

Test/train (75-25 split) and cross-validation were performed on all models. Model prediction performance did not improve greatly using these tests. Model performance resulted in insignificant results when run on the testing data given the smaller sample size.
